---
title: "Create-Final-Sample"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

### Read in the Top List

```{r}
alexa <- read.csv('../../data/alexa-top-sites/alexa-top-sites.csv')
names(alexa)
nrow(alexa)
```

Are all the Alexa Top websites unique?

```{r}
summary(duplicated(alexa %>% select(url)))
```

### Read in the WebShrinker classified websites

```{r}
webshrinker <- read.csv('../../data/final-list/alexa-top-sites-webshrinker.csv')
names(webshrinker)
nrow(webshrinker)
```

### Filter the WebShrinker classification to only retain 

```{r}
webshrinker <- webshrinker %>% filter(category == 'Shopping')
nrow(webshrinker)
```

Are all the Shopping websites unique?

```{r}
summary(duplicated(webshrinker %>% select(url)))
```

### Merge the WebShrinker shopping websites with the original Alexa Top Sites dataset

```{r}
merged_dataset <- merge(alexa, webshrinker, by = 'url')
nrow(merged_dataset)
names(merged_dataset)
```

### What does the distribution of the ranks of the shopping website look like?

```{r}
summary(merged_dataset %>% select(global_rank))
```

### Write the dataset to file

```{r}
write.csv(merged_dataset %>% arrange(global_rank), '../../data/final-list/alexa-top-sites-shopping.csv', quote=FALSE, row.names=FALSE)
```